\thesisTitle

### 2019-10-30 proposal/paper.tex
proposal rc1

Recently \citet{Melnikov2019} have also looked at an alternative class of aggregation functions.
Instead of using fuzzy logic to describe score aggregation, \textit{ordered weighted average} (OWA) operators were used.
OWA aggregators work by sorting the input scores and then weighting them based on their sort position, i.e.\ %
\begin{align*}
	A_{\lambda}(y_1, \dots, y_n) := \sum_{i = 1}^n \lambda_i y_{\pi(i)},
\end{align*}
where $\lambda$ is a weight vector with ${\|\lambda\|}_1 = 1$ and $\pi$ is a sorting permutation of the input scores. % chktex 21
To deal with varying composite sizes $n$ the weights $\lambda_i$ are interpolated using a \textit{basic unit interval monotone} (BUM) function $q: [0, 1] \to [0, 1]$.
It takes constituent positions that are normalized to the unit interval, i.e.\ $\frac{i}{n}$.
The BUM function $q$ then is then used to interpolate a weight for any normalized sort position via $\lambda_i = q(\frac{i}{n}) - q(\frac{i - 1}{n})$.
Therefore the learning objective boils down to optimizing the shape of $q$.
The details of this are left out here.

@@

When looking only at the input and output of the described LTA and graph methods, they share certain similarities.
Both take a variable size and permutation invariant set of constituents/vertices as input and compute an aggregate class or score from it.
There is however a difference between LTA and the described graph methods in the way aggregate scores are computed.

@@

To answer the three research questions, the following approach will be taken.
First the notion of composites and constituents should be generalized based on the definitions found in the previous works on LTA~\cite{Melnikov2016}\cite{Melnikov2019}, so that they are also applicable to graph inputs.
Next the notion of an aggregation function has to be defined and distinguished from the more general concept of an evaluation function (compare \cref{fig:gnnvslta}).

@@

Finally the proposed graph LTA method should be evaluated.
Synthetically generated data or some of the datasets listed in \cref{sec:related-work:tox} could be used for this.
Alternatively the sentiment analysis problem from \textit{natural language processing} (NLP) could be used by interpreting the dependency parse graph of a text as the input and the text's sentiment as its aggregate score.
If time permits, a comparison between the developed graph LTA method and other graph methods should be conducted to demonstrate the potential advantages and disadvantages of the LTA assumptions.

>>>>

Recently \citet{Melnikov2019} have also looked at an alternative class of aggregation functions.
Instead of using fuzzy logic to describe score aggregation, \textit{ordered weighted average} (OWA) operators were used.
OWA aggregators work by sorting the input scores and then weighting them based on their sort position, i.e.\ %
\begin{align*}
	A_{\lambda}(y_1, \dots, y_n) := \sum_{i = 1}^n \lambda_i y_{\pi(i)},
\end{align*}
where $\lambda$ is a weight vector with ${\|\lambda\|}_1 = 1$ and $\pi$ is a sorting permutation of the input scores. % chktex 21
To deal with varying composition sizes $n$ the weights $\lambda_i$ are interpolated using a \textit{basic unit interval monotone} (BUM) function $q: [0, 1] \to [0, 1]$.
It takes constituent positions that are normalized to the unit interval, i.e.\ $\frac{i}{n}$.
The BUM function $q$ then is then used to interpolate a weight for any normalized sort position via $\lambda_i = q(\frac{i}{n}) - q(\frac{i - 1}{n})$.
Therefore the learning objective boils down to optimizing the shape of $q$.
The details of this are left out here.

@@

The described LTA and graph methods are related via their input and output types:
Both take a variable size and permutation invariant set of constituents/vertices as input and compute an aggregate class or score from it.
There is however a difference between LTA and the described graph methods in the way aggregate scores are computed.

@@

To answer the three research questions, the following approach will be taken.
First the notion of compositions and constituents should be generalized based on the definitions found in the previous works on LTA~\cite{Melnikov2016}\cite{Melnikov2019}, so that they are also applicable to graph inputs.
Next the notion of an aggregation function has to be defined and distinguished from the more general concept of an evaluation function (compare \cref{fig:gnnvslta}).

@@

Finally the proposed graph LTA method should be evaluated.
To do so a domain problem has to be found that matches the LTA assumption that composite scores can be expressed as aggregations of local scores.
Synthetically generated data or some of the datasets listed in \cref{sec:related-work:tox} could be considered here.
The sentiment analysis problem from \textit{natural language processing} (NLP) could be an alternative candidate by interpreting the dependency parse graph of a text as the input and the text's sentiment as its aggregate score.
If time permits, a comparison between the developed graph LTA method and other graph methods should be conducted to demonstrate the potential advantages and disadvantages of the LTA assumptions.
